Keyword and Collocation analysis on India-related text of Natural History

### 2023-08-18 paper_quarto.qmd
0818 modification

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of Natural History"
author: "Dawn, Lizao Zhuang (r0914937)"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
code-fold: true
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder. The study focuses on uncovering prominent themes and topics associated with India in the context of the book. The research employs keyword analysis and collocate examination techniques to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
---

```{r setup, include=FALSE}
library('tidyverse')
library('mclm')
library('here')
library('kableExtra')
library('dplyr')
library('ggplot2')
library('leaflet')
options(digits = 3)

@@

```{r}
#| label: fig-geoname
#| fig-cap: Bar Chart for Top 20 Distinct Place Names Mentioned in Natural History
#| fig-cap-location: top
#| warning: false
#| echo: false

@@

top_20_summary_data <- summary_data %>%
  top_n(20, Count) %>%
  ungroup()

ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
  geom_bar(stat = "identity") +
  labs(x = "Place Name", y = "Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

m <- leaflet() %>%
  addTiles() %>%
  addCircleMarkers(
    data = top_20_summary_data,
    lat = ~Lat,
    lng = ~Long,
    radius = sqrt(top_20_summary_data$Count) * 0.8,  
    color = "blue",
    fill = TRUE,
    fillOpacity = 0.6,
    popup = paste("Place Name:", top_20_summary_data$Place_Name, "<br>",
                  "Count:", top_20_summary_data$Count)
  )

@@

The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the [assoc_scores](https://masterclm.github.io/mclm/reference/assoc_scores.html) function. The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2. This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.

@@

Significantly, a substantial number of the keywords in the India-related text revolve around goods, particularly precious stones, suggesting a prominent thematic focus. The presence of keywords such as "beryls", "obsidian", "bdellium", "agates", "callaina", "prasii", "carnelian" and "sandastros" indicates the involvement of various gemstones and goods associated with India. These findings are complemented by the presence of keywords like "condensation", "merchandize" and "peppertree" which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.

Furthermore, the keywords related to rivers in India, such as "ganges", "cophes", "hypasis," and "sacae" indicate their significance as sources of goods or as integral parts of trading routes. Since Pliny the Elder's contextual framework includes critical descriptions of the geographical surroundings like rivers, as evident in his references to the Po River and the Nile River [@pollard2009; @murphy2003], a deeper investigation into the portrayal and role of Indian rivers within this context would provide valuable insights.

Additionally, a notable proportion of the keywords pertain to people, encompassing names, descriptions, and specific historical figures like "megasthenes". This suggests the historical significance of individuals who played a role in trade with India or in documenting and understanding the region.

@@

To analyse the co-text surrounding the term "India," the [surf_cooc](https://masterclm.github.io/mclm/reference/create_cooc.html) function was employed, with "india" designated as the target item for the analysis. And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher. By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.

@@

1.  **Geographical Connections**: The collocates such as "arabia", "ethiopia", "east," "south," "opposite," and "beyond" indicate the geographical relationships and proximity between India and these regions.

2.  **Trading and Imports**: The presence of collocates like "imported", "produces", "produce" and "nations" suggests that India had a significant role in trade and the importation of goods. It also implies that India was known for producing various commodities that were sought after by other nations.

3.  **Boundaries and Borders**: The collocates "boundary," "set" and "part" indicate the existence of defined boundaries or borders related to India. This suggests that there were recognized territorial demarcations associated with India during the referenced period.

>>>>

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of Natural History"
author: "Dawn, Lizao Zhuang (r0914937)"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
echo: false
code-link: true
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder. The study focuses on uncovering prominent themes and topics associated with India in the context of the book. The research employs keyword analysis and collocate examination techniques to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
---

```{r setup, include=FALSE}
library('tidyverse')
library('mclm')
library('here')
library('kableExtra')
library('leaflet')
options(digits = 3)

@@

```{r}
#| label: fig-geoname
#| fig-cap: Bar chart for top 20 distinct place names mentioned in *Natural History*
#| fig-cap-location: top
#| warning: false
#| echo: false

@@

# Create a bar chart using ggplot2
top_20_summary_data <- summary_data %>%
  top_n(20, Count) %>%
  ungroup()

ggplot(top_20_summary_data, aes(x = reorder(Place_Name, -Count), y = Count)) +
  geom_col() +
  labs(x = "Place name", y = "Number of occurrences") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

m <- leaflet() %>%
  addTiles() %>%
  addCircleMarkers(
    data = summary_data,
    lat = ~Lat,
    lng = ~Long,
    radius = sqrt(summary_data$Count) * 0.8,  # Adjust the scaling factor as needed
    color = "blue",
    fill = TRUE,
    fillOpacity = 0.6,
    popup = paste("Place name:", summary_data$Place_Name, "<br>",
                  "Number of occurences:", summary_data$Count)
  )

@@

The frequency lists for the **target corpus** (India-related texts) and **reference corpus** (whole text) are generated respectively, and the association scores are calculated through the `mclm::assoc_scores()` function. The association score is filtered based on the criteria of both PMI and $G^2$ scores, requiring a minimum score of 2. This criterion ensures that the selected words have a probability at least four times higher than the overall data, along with statistically significant supporting evidence [@methods], allowing to identify the most statistically significant keywords in India-related texts when compared to the reference corpus.

@@

Significantly, a substantial number of the keywords in the India-related text revolve around goods, particularly precious stones, suggesting a prominent thematic focus. The presence of keywords such as *beryls*, *obsidian*, *bdellium*, *agates*, *callaina*, *prasii*, *carnelian* and *sandastros* indicates the involvement of various gemstones and goods associated with India. These findings are complemented by the presence of keywords like *condensation*, *merchandize* and *peppertree* which suggest the production and trade of goods between the Roman Empire and the Indian regions during that era.

Furthermore, the keywords related to rivers in India, such as *ganges*, *cophes*, *hypasis*, and *sacae* indicate their significance as sources of goods or as integral parts of trading routes. Since Pliny the Elder's contextual framework includes critical descriptions of the geographical surroundings like rivers, as evident in his references to the Po River and the Nile River [@pollard2009; @murphy2003], a deeper investigation into the portrayal and role of Indian rivers within this context would provide valuable insights.

Additionally, a notable proportion of the keywords pertain to people, encompassing names, descriptions, and specific historical figures like *megasthenes*. This suggests the historical significance of individuals who played a role in trade with India or in documenting and understanding the region.

@@

To analyse the co-text surrounding the term "India," the `mclm::surf_cooc()` function was employed, with "india" designated as the target item for the analysis. And following the same criteria as the previous keyword analysis, the collocation scores were filtered of having both PMI and G_signed scores of 2 or higher. By employing this approach, the prominent collocates of "india" were identified, providing a tangible understanding of the prevailing discourse and potentially reflecting Pliny the Elder's perspective on the region.

@@

1.  **Geographical Connections**: The collocates such as *arabia*, *ethiopia*, *east*, *south*, *opposite*, and *beyond* indicate the geographical relationships and proximity between India and these regions.

2.  **Trading and Imports**: The presence of collocates like *imported*, *produces*, *produce* and *nations* suggests that India had a significant role in trade and the importation of goods. It also implies that India was known for producing various commodities that were sought after by other nations.

3.  **Boundaries and Borders**: The collocates *boundary*, *set* and *part* indicate the existence of defined boundaries or borders related to India. This suggests that there were recognized territorial demarcations associated with India during the referenced period.
